%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Turor, CSYS5010} % Job title
    {Sydney University} % Organization
    {Sydney, NSW, Australia} % Location
    {August - December 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item Marking, responding to questions, Tutorials, assisting lecturer.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineer, Artificial Intelligence Group} % Job title
    {Adtran} % Organization
    {Huntsville, Alabama, USA} % Location
    {2017-2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item Artificial Intelligence applied research with a focus on troubleshooting layer 1 and layer 2 issues on GPON, NGPON2, and VDSL deployments.
\item Artificial Intelligence platform development
\item Work includes Generative Adversarial Networks, Autoencoders, Support Vector Machines, Decision Trees, Bayes Nets, Reinforcement
\item Learning, and Feed Forward Neural Network Classifiers
\item  Won Innovation and Improvement Week Competition at ADTRAN three out of four times.
\item  Work led to the filing of two patents (currently pending).
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, Reusable Component Development} % Job title
    {} % Organization
    {} % Location
    {2016-2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item  Tool Development for C.I. Pipeline
\item  Development of re-usable components common across multiple products. Work includes development of ADTRAN’s Mosaic OS Linux distribution and NETCONF stack.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, Embedded Systems Development} % Job title
    {} % Organization
    {} % Location
    {2011-2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item Developed and maintained AOS (ADTRAN Operating System) including Kernel and Network Devices
\item Developed and maintained network protocols and network interfaces. Work includes BGP, OSPF, Metro Ethernet, IPSec, and Network Function Virtualization.
\item This work led to the filing of a patent (currently pending) related to IPSec Selectors
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Auburn University} % Organization
    {Auburn, Alabama, USA} % Location
    {2009-2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item Worked on a computational ethnography tool written in python
\item Automatic hypothesis generation and experiment testing using meta-heuristics such as Genetic Programming and Ant Colony Optimization.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {Auburn University} % Organization
    {Auburn, Alabama, USA} % Location
    {2008-2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item Social network graph visualizations
\item Preliminary data analysis using metrics such as centrality and density
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
